Mortality Trends Among Shelter Residents in Toronto from 2007 to 2024

### 2024-09-27 paper/paper.qmd
File folders changed

---
title: "Mortality Trends Among Shelter Residents in Toronto: A Longitudinal Study from 2007 to 2024"
author: 
  - Fangning Zhang
thanks: "Code and data are available at: https://github.com/FangningZhang81/Deaths-of-Shelter-Residents."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
#hide the code in the PDF

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows:@sec-data describes the data sources, tools, cleaning process, visualization, result and related datasets; and @sec-discussion summarizes the key findings, interprets the results, discusses limitations, and suggests directions for future research.

@@

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

>>>>

---
title: "Mortality Trends Among Shelter Residents in Toronto from 2007 to 2024"
author: 
  - Fangning Zhang
thanks: "Code and data are available at: https://github.com/FangningZhang81/Deaths-of-Shelter-Residents."
date: today
date-format: long
abstract: "This study conducts a series of analyses of mortality among shelter residents in Toronto from 2007 to 2023, focusing on overall trends, gender differences, and seasonal variations. The results indicate a concerning increase in deaths starting from 2019, particularly among males. The number of deaths during the winter months is higher compared to other months. Understanding the mortality of shelter residents is crucial for formulating effective social policies, improving shelter services, and enhancing the health and well-being of vulnerable groups."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
#hide the code in the PDF

@@

The remainder of this paper is structured as follows: @sec-data describes the data sources, tools, cleaning process, visualization, result and related datasets; and @sec-discussion summarizes the key findings, interprets the results, discusses limitations, and suggests directions for future research.

@@
